Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-04 document/ms.tex
Add a condensed abstract

\shorttitle{\name IGRINS spectroscopy}

@@

\begin{abstract}
We interpret the high resolution near-IR spectra of LkCa 4.  We used the instrument IGRINS.
\end{abstract}

>>>>

\shorttitle{\name Starspots on LkCa 4}

@@

\begin{abstract}
The weak-lined T-Tauri star LkCa 4 has no evidence for IR excess, accretion, or nearby companions, and shows exceptionally large photometric modulation attributable to star spots, making it an ideal testbed for measuring starspot properties.  Infrared spectral features in high resolution data indicate that 70-80\% of the surface is covered in 2700$-$3000 K effective temperature regions at the epoch of the observation.  The photometric phase curve is scaled to this filling factor to construct the fill-factor-as-a-function-of-phase.  The SED, color variability, and low-resolution optical/IR spectroscopy are registered to filling factor at their epochs, confirming the large filling factor and temperature contrast of the starspots through time.  The revised effective temperature and luminosity make LkCa4 appear much lower mass and much younger when placed on a pre-main sequence HR diagram, compared to previous estimates based only on optical spectroscopy and not taking into account the large coverage fraction of cool spots.
\end{abstract}
